Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-14 icse/paper.tex
cloneRef URL

\section{CloneRefactor}
% NEED TO EXPLAIN WHY DO CURRENT DETECTION TOOLS NOT SUFFICE
% The tool: Detect Clones, Map Context, Refactor.
To automate the process of refactoring clones, we propose a tool named CloneRefactor. This tool goes through a 3-step process in order to refactor clones. This process is displayed in figure \ref{fig:clonerefactorflow}.
\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/flow}
  \caption{Simple flow diagram of CloneRefactor.}
  \label{fig:clonerefactorflow}
\end{figure}
In this section, we explain each of these steps.

@@

\subsubsection{Extract Method}
There are several influencing factors that may obstruct the possibility to extract code to a new method:
\begin{itemize}
    \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement.
    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:contents}, the ``Extract Method'' refactoring technique cannot be applied.
    \item \textbf{Returns multiple values}: If a clone modifies or declares multiple pieces of data that it should return.
    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method. Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
\end{itemize}
Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor. CloneRefactor only refactors the clones that \textit{Can Be Extracted}.

\subsubsection{AST Transformation}
Explain what AST transformations I do to apply the refactorings.

>>>>

\section{CloneRefactor}
% NEED TO EXPLAIN WHY DO CURRENT DETECTION TOOLS NOT SUFFICE
% The tool: Detect Clones, Map Context, Refactor.
To automate the process of refactoring clones, we propose a tool named CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}. This tool goes through a 3-step process in order to refactor clones. This process is displayed in Fig.~\ref{fig:clonerefactorflow}.
\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/flow}
  \caption{Simple flow diagram of CloneRefactor.}
  \label{fig:clonerefactorflow}
\end{figure}
In this section, we explain each of these steps.

@@

\subsubsection{Extract Method}
% Show my categories to show what clones can be dealt with by method extraction.
There are several influencing factors that may obstruct the possibility to extract code to a new method:
\begin{itemize}
    \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement.
    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:contents}, the ``Extract Method'' refactoring technique cannot be applied.
    \item \textbf{Returns multiple values}: If a clone modifies or declares multiple pieces of data that it should return.
    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method. Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
\end{itemize}
Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor. CloneRefactor only refactors the clones that \textit{Can Be Extracted}.

\subsubsection{AST Transformation}
% Explain what AST transformations I do to apply the refactorings.
